Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/results.tex
missed two captions

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{validation_FOA_fig2a_Ellis.pdf} 
    \caption{Validation against experiments in figure 2a of Ellis 2016, using first order approximation}
    \label{fig:val_2a}
 \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{replication_FOA_fig2a_Ellis.pdf} 
    \caption{Replication of simulations in figure 2a of Ellis 2016, using first
     order approximation}
    \label{fig:rep_2a}
 \end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{validation_FOA_fig2a_Ellis.pdf} 
    \caption{Validation against experiments in Figure 2a of Ellis, et al., 2016, using the first-order correction, as explained in the text.}
    \label{fig:val_2a}
 \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{replication_FOA_fig2a_Ellis.pdf} 
    \caption{Replication of the simulations in Figure 2a of Ellis et al., 2016, using the first-order correction, as explained in the text.}
    \label{fig:rep_2a}
 \end{figure}
